A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-06-07 04_Severity_MetaAnalysis.Rmd
edit sensitivity plot line thickness and scale

sensitiviy_df %>%
   ggplot(aes(Tnum, estimates, colour = treat))+
   geom_line()

sensitiviy_df %>%
   ggplot(aes(Tnum, p, colour = treat))+
   geom_line()

>>>>

sensitiviy_df %>%
   ggplot(aes(Tnum, estimates, colour = treat))+
   geom_line(size = 1)

sensitiviy_df %>%
   ggplot(aes(Tnum, p, colour = treat))+
   geom_line(size = 1)+
   scale_y_log10()
